%--------------------------------------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%--------------------------------------------------------------------------------------------------------------------

\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks=true}

\name{Pablo D. Pusiol}
\address{Citizenship: Italian \& Argentinian \quad|\quad Alta Gracia, Córdoba, Argentina}
\address{pablo.pusiol@gmail.com \quad|\quad +54 9 351 622-7364}

\begin{document}

%--------------------------------------------------------------------------------------------------------------------
% PROFESSIONAL PROFILE
%--------------------------------------------------------------------------------------------------------------------
\begin{rSection}{Profile}
Deep-Learning-focused R&D Director with 10+ years of experience in Edge AI, NMR sensor signal processing, and embedded deep learning. Proven track record bridging academic collaborations (CONAE, INRIA) and industry deployments (Spinlock, Activity Recognition Inc.), leading cross-functional teams to deliver high-throughput, real-time analytic solutions that reduce costs, enhance quality control, and drive product innovation.
\end{rSection}

%--------------------------------------------------------------------------------------------------------------------
% CORE COMPETENCIES
%--------------------------------------------------------------------------------------------------------------------
\begin{rSection}{Core Competencies}
\begin{tabular}{@{}p{2in}p{2in}@{}}
Edge AI \& Embedded DL & NMR Sensor Signal Processing \\
1D/2D Convolutional Architectures & Cross-functional Leadership \\
Product Roadmapping \& Strategy & Academic \& Industry Partnerships \\
Quantitative Impact Analysis & Regulatory \& Quality Management \\
\end{tabular}
\end{rSection}

%--------------------------------------------------------------------------------------------------------------------
% EDUCATION SECTION
%--------------------------------------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf M. Sc. in Computer Science (2012--2014)} \\[-0.5ex]
FaMAF -- UNC, Córdoba, Argentina \quad|\quad Thesis: 10.0/10.0\\
Curriculum: Remote sensing \& satellite imagery (CONAE), advanced computer vision, deep learning.\\
"Deep Learning for Scene Semantics \& Activity Recognition in Sports" — applied CNNs to tennis broadcasts to classify semantic events. \href{http://repositoriosdigitales.mincyt.gob.ar/vufind/Record/RDUUNC_0aec6058e869999c7224655c3c2c98bf}{Reference}.\\[1ex]
{\bf B. Sc. in Computer Science (2009--2011)} \\[-0.5ex]
FaMAF -- UNC, Córdoba, Argentina.
\end{rSection}

%--------------------------------------------------------------------------------------------------------------------
% PROFESSIONAL EXPERIENCE SECTION
%--------------------------------------------------------------------------------------------------------------------
\begin{rSection}{Professional Experience}

\begin{rSubsection}{Spinlock SRL}{New Technologies Director \quad|\quad Córdoba, AR \quad|\quad May 2017--Present}{
\item Lead a team of 6 engineers and data scientists in developing Edge AI solutions for industrial and healthcare applications.
\item Architected and deployed 1D CNN pipelines achieving 70K seeds/hour throughput, reducing manual QC costs by 30%.
\item Oversaw Noctua spinoff: secured PoC pilots at three 500-bed university hospitals (Córdoba, Buenos Aires, Catalunya), targeting a projected 25% reduction in in-hospital falls.
\item Drove technical strategy for all user & research applications: C#, Python, TensorFlow, PyTorch, .NET; resulting in a 40% decrease in calibration drift.
\item Delivered inline NMR spectrometer for nutritional analysis, deployed in Houston (PepsiCo), boosting production line efficiency by 15%.
\item Presented deep-learning-based auto-calibration method at IAPG 2019; published patent pending on style-transfer calibration.
}

\begin{rSubsection}{Activity Recognition Inc.}{Machine Learning Engineer \& Co-lead \quad|\quad Mountain View, CA \quad|\quad Jan 2015--Apr 2017}{
\item Co-led design and deployment of a web-based elder-care recommendation engine live in 5 cities; increased user engagement by 50%.
\item Developed Thermix far-infrared monitoring app (FLIR Bring the Heat 2015 Best Software Award).
\item Delivered on-device CNN inference apps (VDO, Bestie) enabling real-time media processing on iPhone 4-class hardware.
}

\begin{rSubsection}{INRIA}{Research Intern \quad|\quad Sophia Antipolis, FR \quad|\quad Apr 2014--Oct 2014}{
\item Implemented deep-learning pipelines for RGB-D people detection; integrated into EU Dem@care project for long-term behavior analysis.
}

\end{rSection}

%--------------------------------------------------------------------------------------------------------------------
% SELECTED AWARDS & PUBLICATIONS
%--------------------------------------------------------------------------------------------------------------------
\begin{rSection}{Awards \& Publications}
\begin{itemize}
  \item Best Software Award, FLIR Bring the Heat, San Francisco 2015.
  \item Pusiol, G. T. Pusiol, et al. "Deep Learning for Scene Semantics in Sports." [Conference Paper].
  \item Patent Pending: "Style-Transfer-Based Calibration of NMR Sensors."
\end{itemize}
\end{rSection}

%--------------------------------------------------------------------------------------------------------------------
% TECHNICAL SKILLS SECTION
%--------------------------------------------------------------------------------------------------------------------
\begin{rSection}{Technical Skills}
\begin{tabular}{@{}p{2in}p{2in}@{}}
Languages: C#, Python, Objective-C & Frameworks: .NET, TensorFlow, PyTorch\\
Tools: DVC, JupyterLab, Git & Platforms: AWS, Docker, Kubernetes
\end{tabular}
\end{rSection}

%--------------------------------------------------------------------------------------------------------------------
% LANGUAGES & INTERESTS
%--------------------------------------------------------------------------------------------------------------------
\begin{rSection}{Languages \& Interests}
Spanish (native), English (fluent), French (intermediate). Avid triathlete and tennis player.
\end{rSection}

\end{document}
